Data- and Systems Paper : Finding Amsterdam

### 2016-05-27 milestone4/paper/paper.tex
results table

Since the out-degree distribution has a heavy tail, we select $threshold = 10, 20, 40, 75$ as approximate quartiles. As you see here the number of triples grows linearly .

\begin{table}[h]
	\begin{center}
		\begin{tabular}{| l | c | c |}
			\hline
			\textbf{Threshold} & \textbf{n of triples} & \textbf{Time} \\ \hline
			10 &  505,993 & 00:00:03.663 \\ \hline
			20 & 34,785 & 00:00:00.294 \\ \hline
			40 & 25,602 & 00:00:00.200 \\ \hline
			75 & 17,359 & 00:00:00.128 \\ \hline
		\end{tabular}
		\caption{Statistics for subgraph formation.}
		\label{frequency_table}
	\end{center}
\end{table}

@@

\section{Results and Discussion}
When ran against the whole \texttt{datset} we obtain 31 results.

- results when random

- results when "smart"

>>>>

Since the out-degree distribution has a heavy tail, we select $threshold = 10, 20, 40, 75$ as approximate quartiles. As you see in Table \ref{subgraph_table} the number of triples grows linearly .

\begin{table}[h]
	\begin{center}
		\begin{tabular}{| l | c | c |}
			\hline
			\textbf{Threshold} & \textbf{n of triples} & \textbf{Time} \\ \hline
			10 &  505,993 & 00:00:03.663 \\ \hline
			20 & 34,785 & 00:00:00.294 \\ \hline
			40 & 25,602 & 00:00:00.200 \\ \hline
			75 & 17,359 & 00:00:00.128 \\ \hline
		\end{tabular}
		\caption{Statistics for subgraph formation.}
		\label{subgraph_table}
	\end{center}
\end{table}

@@

\section{Results and Discussion}
\begin{table}[h]
	\begin{center}
		\begin{tabular}{| l | c | c |}
			\hline
			\textbf{Subgraph} & \textbf{Results count} & \textbf{Time in microseconds} \\ \hline
			out-10 & 1144 & -343883 \\ \hline
			out-20 & 99 & 138225 \\ \hline
			out-40 & 95 & 59086 \\ \hline
			out-75 & 94 & 51484 microseconds \\ \hline
		\end{tabular}
		\caption{Statistics for subgraph formation.}
		\label{subgraph_table}
	\end{center}
\end{table}
